A finite-state morphological transducer for Kyrgyz

### 2012-03-14 paper/paper.tex
restructure acknowledgement of Tolgonay

We would like to thank: the Google Summer of Code 2011, which supported the development of the Turkish$\rightarrow$Kyrgyz MT system this transducer was designed for; Tolgonay Kubatova for native speaker intuitions of Kyrgyz; and the anonymous reviewers for comments on how to improve the manuscript.  This work has been partially funded by Spanish Ministerio de Ciencia e Innovación through project TIN2009-14009-C02-01.

>>>>

We would like to thank: the Google Summer of Code 2011, which supported the development of the Turkish$\rightarrow$Kyrgyz MT system this transducer was designed for; Tolgonay Kubatova for additional native-speaker insight on Kyrgyz and all the ways she's supported the authors and this project; and the anonymous reviewers for comments on how to improve the manuscript.  This work has been partially funded by Spanish Ministerio de Ciencia e Innovación through project TIN2009-14009-C02-01.
